Distributed Range-Only Localisation that Preserves Sensor and Navigator Privacies

### 2022-10-11 main.tex
Minor rewording to make the manuscript fit on 12 pages again Updated and added diff file to the response

\subsection{Notation}
Throughout this work, we make use of the following notation. Underlined characters, $\vec{a}$, denote vectors, uppercase bold characters, $\mat{A}$, denote matrices. $\mat{A}^{-1}$ is the matrix inverse while $\mat{A}^\top$ is its transpose. The expected value of a random variable is denoted by $\mathsf{E}[\cdot]$, while the variance of a random scalar and covariance of a random vector by $\mathsf{Var}[\cdot]$ and $\mathsf{Cov}[\cdot]$, respectively. $|a|$ denotes absolute value, $\lVert\vec{a}\rVert$ the vector norm, $\{\dots\}$ is used for sets and $\langle\dots\rangle$ for ordered sequences. When estimating a state, notation $\hat{\vec{x}}_{k|e}$ will denote an estimate of $\vec{x}$ at timestep $k$ given measurements from timesteps up to and including timestep $e$. When discussing cryptography, $\mathcal{E}_{sk}(\cdot)$ and $\mathcal{D}_{sk}(\cdot)$ will denote encryption and decryption with key $sk$, respectively, with $sk$ ommited when inferrable from context. $\mathbb{Z}_N$ is used for the set of integers modulo $N$ and $\mathbb{Z}^*_N$ for its multiplicative group. $\mathsf{lcm}(\cdot,\cdot)$ is the lowest common denominator, $\|$ is the binary concatination operator, and the term \textit{negligible function} refers to its cryptographic definition in \cite{katzIntroductionModernCryptography2008}.

@@

Before giving a formal definition for the construction and security of our desired encryption scheme, we make the following assumptions on the capabilities of the participants.
\begin{LaTeXdescription}
    \item[Global Navigator Broadcast] We assume that broadcast information from the navigator is received by \textit{all} sensors involved in the protocol.
    \item[Consistent Navigator Broadcast] We assume that broadcast information from the navigator is received equally by all sensors. This means the navigator may not send different weights to individual sensors during a single instance $t$.
    \item[Honest-but-Curious Attackers] We adopt the honest-but-curious attacker model for all corrupted parties that an attacker controls, meaning that the navigator and sensors follow the localisation procedure correctly but attackers may store or use any gained sensitive information.
\end{LaTeXdescription}
We justify the global broadcast assumption by noting that any subset of sensors within the range of the navigator can be considered a group and treated as the global set during estimation, generalising the method, while the wide-spread use of cheap non-directional antennas supports the assumption of consistent broadcasts. The final assumption refers to the known problem of misbehaving sensors \cite{lazosSeRLocSecureRangeindependent2004,ben-galOutlierDetection2005}, often requiring additional complicated detection mechanisms, and will not be considered in this work.

>>>>

\subsection{Notation}
Throughout this work, we make use of the following notation. Underlined characters, $\vec{a}$, denote vectors, uppercase bold characters, $\mat{A}$, denote matrices. $\mat{A}^{-1}$ is the matrix inverse while $\mat{A}^\top$ is its transpose. The expected value of a random variable is denoted by $\mathsf{E}[\cdot]$, while the variance of a random scalar and covariance of a random vector by $\mathsf{Var}[\cdot]$ and $\mathsf{Cov}[\cdot]$, respectively. $|a|$ denotes absolute value, $\lVert\vec{a}\rVert$ the vector norm, $\{\dots\}$ is used for sets and $\langle\dots\rangle$ for ordered sequences. When estimating a state, notation $\hat{\vec{x}}_{k|e}$ will denote an estimate of $\vec{x}$ at timestep $k$ given measurements from timesteps up to and including timestep $e$. When discussing cryptography, $\mathcal{E}_{sk}(\cdot)$ and $\mathcal{D}_{sk}(\cdot)$ will denote encryption and decryption with key $sk$, respectively, with $sk$ ommited when inferrable from context. $\mathbb{Z}_N$ is used for the set of integers modulo $N$ and $\mathbb{Z}^*_N$ for its multiplicative group. $\mathsf{lcm}(\cdot,\cdot)$ is the lowest common denominator, $\|$ is the binary concatination operator, and the term \textit{negligible function} refers to its definition in \cite{katzIntroductionModernCryptography2008}.

@@

Before giving a formal definition for the construction and security of our desired encryption scheme, we make the following assumptions on the capabilities of the participants.
\begin{LaTeXdescription}
    \item[Global Navigator Broadcast] We assume that broadcast information from the navigator is received by \textit{all} sensors involved in the protocol.
    \item[Consistent Navigator Broadcast] We assume that broadcast information from the navigator is received equally by all sensors. This means the navigator may not send different weights to individual sensors during a single instance $t$.
    \item[Honest-but-Curious Attackers] We adopt the honest-but-curious attacker model. The navigator and sensors are corruptable but follow the localisation procedure correctly, while attackers may use any gained sensitive information.
\end{LaTeXdescription}
We justify the global broadcast assumption by noting that any subset of sensors within the range of the navigator can be considered a group and treated as the global set during estimation, generalising the method, while the wide-spread use of cheap non-directional antennas supports the assumption of consistent broadcasts. The final assumption refers to the known problem of misbehaving sensors \cite{lazosSeRLocSecureRangeindependent2004,ben-galOutlierDetection2005}, often requiring additional complicated detection mechanisms, and will not be considered in this work.
